# Python {-}

```{r,include=FALSE}
library(reticulate)
use_python("C:\\Users\\KINGLE~1\\AppData\\Local\\Programs\\Python\\Python38\\python.exe")
```

## Getting Started

The world confronts us. Make decisions we must. 

### Installing Python 3 and Jupyter Notebook 

Throughout this book, we assume that you are using Python 3 and Jupyter Notebook. Python is a programming language that runs computations, and Jupyter Notebook is an open-sourced web-based *integrated development environment (IDE)* that provides an easy-to-use interactive data science environment.

Download and install both Python 3 and Jupyter Notebook on your computer.

1.**Do this first**: [Download and install Python 3.](https://www.python.org/downloads/)
2.**Follow these steps in order to download and install Jupyter Notebook**: 
[Download and install Anaconda](https://www.anaconda.com/products/individual) to your computer. Search for ‘Anaconda Navigator’ in the search bar and click it. 
Navigator will look much-or-less like the image below. Although Because we have already installed Jupyter Notebook, the button below it says ‘Launch’ instead of ‘Install,’ you will see that button as ‘Install.’ Once you see this page, click ‘Install’ Jupyter Notebook.  

```{r, include=FALSE}
# <!-- Atilla: I will put the anaconda image here. 
# <!-- Atilla: First, however, create an image folder in github. 
```

### Using Python 3 via Jupyter Notebook 

For most cases, we won’t be using Python directly but rather we will use Jupyter Notebook’s interface. After you install Python 3 and Jupyter Notebook on your computer, you’ll have two new programs (also called applications) you can open. Always work in Jupyter Notebook and not directly in the Python 3 application.
 
Let’s begin with getting familiar with Jupyter Notebook. Open up Jupyter Notebook. You should see a section with file names and a few command buttons, such as ‘Quit’ and ’New.’ To create a new Python 3 project, you should click on the ‘New’ button and then choose the ‘Python 3’ Notebook option, as shown below. If you create a project, it will be saved and visible among the files below. For accessibility, we recommend creating a folder for your projects and save your projects there.

```{r, include=FALSE}
# <!-- Atilla: I will put the image of Jupyter Notebook interface here.
```

Jupyter notebooks exist of a series of cells that provide different uses. Three cell types that are often used are given below. 
1. Code cell is the cell you write the code in.
2. Markdown is the text cell.
3. Heading is the cell you use as header and title. 

```{r, include=FALSE}
# <!-- Atilla: I will put the image of cell types in Jupyter here. 
```

The cell types can be chosen from the dropdown as shown above. 
 
Different than other IDEs, Jupyter Notebook does not show the list of environment variables in a tab. Instead, to get the list of variables in a notebook, write the following code in a code cell.

```{python,eval=FALSE}
%whos
```

An example of the use of `%whos` is shown below. 

```{python,eval=FALSE}
In  [2] :  x = 5
           Y = “string” 
           %whos 

```

In a notebook with the above variables, if you call %whos, the output should look like this.

```{python,eval=FALSE}
Out  [2] : Variable   Type    Data/Info
           ----------------------------
              x       int     5
              y       str     string

```

### Package Installation 

Python *packages*, also known as *libraries*, extend the power of Python by providing additional functions and data.
Python is like a new mobile phone: while it has a certain amount of features when you use it for the first time, it doesn’t have everything. Python packages are like the apps you can download onto your phone.
Consider an analogy to Instagram. If you have a new phone and want to share a photo with friends. You need to:
1. *Install the app*: Since your phone is new and does not include the Instagram app, you need to download the app. You do this only once. (You might need to do this again in the future when there is an update to the app.)
2. *Open the app*: After you’ve installed Instagram, you need to open it. You need to do this every time you use the app.
 
The process is very similar for a Python package. You need to:
1. *Install the package*: This is like installing an app on your phone. Most packages are not installed by default when you install Python. Thus, if you want to use a package for the first time, you need to install it. Once you’ve installed a package, you likely won’t install it again unless you want to update it to a newer version.
2. *“Load” the package*: “Loading” a package is like opening an app on your phone. Packages are not “loaded” by default when you start Jupyter Notebook. You need to “load” each package you want to use every time you restart Jupyter.
 
 
One way to install the package is from the command prompt/terminal. For example, to import numpy- a popular library used to statistically analyse a data set- Type the following code to the command prompt. 

```{python,eval=FALSE}
pip install numpy
```

After writing this line of code in the command prompt, hit enter on your keyboard. You should also install two more packages we will use in earlier chapters of Primer: “Matplotlib’ and ‘Pandas.’

### Package loading

To use the installed packages, we have to load them, and we do this by using the import statement. If you import a package in one cell, you do not need to import it again in another cell as long as you do not restart the Jupyter Notebook.
For example, to load the numpy package, run the following code in a code cell in the notebook.  

```{python,eval=FALSE}
import numpy as np
```

To save time, when we want to load a library, we usually save it under a different name. Thus, ‘as np’ is generally called when importing numpy. 

### Package Use

You have to load each package you want to use every time you start Jupyter Notebook. If you don’t load a package before attempting to use one of its features, you will see an error message like:

```{python,eval=FALSE}
NameError: name 'numpy' is not defined
```

With this Error, Python is telling you that you are trying to use a function that has not been loaded yet. If you load the package and then run the code, it will work without error, as shown below. 

```{r, include=FALSE}
# <!-- Atilla: I will put the image of a simple numpy function I ran.  
```

### Summary

You should have done the followings: 
* Installed the latest versions of Python 3 and Jupyter Notebook.
* Installed the following three packages: 
  1. Numpy
  2. Matplotlib
  3. Pandas


```


## Visualization


## Wrangling



